UKB Models

### 2023-10-12 ukb_curation-eda.Rmd
moving site sims to EDA rmd

>>>>

## Simulate Sites
Dividing each subject into 3 sites (A, B, and C) with M:F ratios of 1:1, 1:4, and 4:1

```{r}
set.seed(1010101)
sim.site.list <- c("Site_A", "Site_B", "Site_C")
n_female <- table(ukb_df_age.filt$sex)["Female"]
n_male <- table(ukb_df_age.filt$sex)["Male"]

# Sample probabilities
male_prob <- c(0.33, 0.0825, 0.5875)
female_prob <- c(0.33, 0.5875, 0.0825)

# Separate samples for males and females
sampled_males <- sample(sim.site.list, size = n_male, replace = TRUE, prob = male_prob)
sampled_females <- sample(sim.site.list, size = n_female, replace = TRUE, prob = female_prob)

ukb_df_sites <- ukb_df_age.filt %>%
  mutate(sim.site = as.factor(ifelse(sex == "Male", sampled_males, sampled_females)))

#write out
write_csv(ukb_df_sites, file="data/ukb_CN_data_simsites.csv")
```

```{r}
table(ukb_df_sites$sim.site)
table(ukb_df_sites$sim.site, ukb_df_sites$sex)
sum(is.na(ukb_df_sites$sim.site)) #all subj assigned to sites
anova(lm(age_days ~ sim.site, ukb_df_sites))
```

Need to come up with cleaner way to do this...

```{r}
site_sum_df <- ukb_df_sites %>%
  group_by(sim.site) %>%
  summarise(proportion_male = mean(sex == "Male"),
            min_age = min(age_days), max_age = max(age_days), mean_age = mean(age_days), 
            var_gmv = var(GMV), var_wmv=var(WMV), var_sgmv=var(sGMV), var_ven = var(Ventricles),
            sd_below.gmv = mean(GMV) - sd(GMV), sd_above.gmv = mean(GMV) + sd(GMV))
```

Center and visualize distributions

```{r}
ukb_sites_sex.centered <- ukb_df_sites %>%
  group_by(sex) %>%
  mutate_if(is.numeric, funs(scale(., center=TRUE, scale=FALSE))) %>%
  ungroup()
```

```{r}
# Generate histograms (mean-centered w/in sex)
global_site_plots <- plot.hist.by.sex(ukb_sites_sex.centered, vol_list_global, facet_fac = "sim.site")

# Print or display the histograms
for (pheno in vol_list_global) {
  print(global_site_plots[[pheno]])
}
```

Look at uncentered distributions across sites
```{r}
ggplot(ukb_df_sites, aes(x=GMV)) + 
 geom_histogram(aes(y=after_stat(density)))+
 geom_density(alpha=.2) +
  geom_vline(aes(xintercept=(mean(GMV)+sd(GMV)))) +
  geom_vline(aes(xintercept=(mean(GMV)-sd(GMV))))

ggplot(ukb_df_sites, aes(x=GMV)) + 
 geom_histogram(aes(y=after_stat(density)))+
 geom_density(alpha=.2) +
  geom_vline(aes(xintercept=(mean(GMV)+sd(GMV)))) +
  geom_vline(aes(xintercept=(mean(GMV)-sd(GMV)))) +
  facet_wrap(~sim.site)
```

```{r}
centered.site_df <- ukb_df_sites %>%
  group_by(sim.site) %>%
  mutate_if(is.numeric, funs(scale(., center=TRUE, scale=FALSE))) %>%
  ungroup()

centered.site_sum_df <- centered.site_df %>%
  group_by(sim.site) %>%
  summarise(sd_below.gmv = mean(GMV) - sd(GMV), sd_above.gmv = mean(GMV) + sd(GMV))

ggplot() + 
 #geom_histogram(aes(x=centered.site_df$GMV, y=after_stat(density), fill=centered.site_df$sim.site, color=centered.site_df$sim.site), alpha = .2)+
 geom_density(aes(x=centered.site_df$GMV, fill=centered.site_df$sim.site, color=centered.site_df$sim.site), alpha=.4) +
  geom_vline(aes(xintercept=centered.site_sum_df$sd_below.gmv, color=centered.site_sum_df$sim.site)) +
  geom_vline(aes(xintercept=centered.site_sum_df$sd_above.gmv, color=centered.site_sum_df$sim.site))
```

## ComBat

And now, to combat the data across the simulated sites!
